Commutative character sheaves and geometric types for supercuspidal representations

### 2017-05-05 Geometric types.tex
Talking with David.

In this section we give an equivalence of categories between $\CS(G\ab)$ and $\CSab(G)$ and use it to describe
the pullback functor $q^* : \CS(G\ab) \to \CS(G)$ in terms of the forgetful functor $\CSab(G) \to \CS(G)$.
We start with a method that will allow us to situate the diagram in Definition \ref{def:CCS} within $\CSab(G \times G)$.

In order to study commutative character sheaves, we need some auxiliary categories.
\begin{itemize}
\item Let $\Loc(G)$ and $\Loc(G\ab)$ be the categories of local systems on $G$ and $G\ab$, respectively.
\item Let $\Loc_{G\der}(G)$ be the category of $G\der$-equivariant local systems on $G$, whose definition we now recall.
Let $n : G\der\times G\to G$ be the restriction of $m : G\times G\to G$ to $G\der\times G$,
let $p_n : G\der\times G \to G$ be projection to the second component, and let $s: G \to G\der\times G$ be given by $s(g) = (1,g)$.
Objects in $\Loc_{G\der}(G)$ are pairs $(\cs{L},\nu)$ where $\cs{L}$ is a local system on $G$ and
$\nu : n^*\cs{L} \to p^*\cs{L}$ is an isomorphism such that the following two diagrams commute.
\[
\begin{tikzcd}
s^*n^*\cs{L} \arrow{r}{s^*(\nu)} & s^*p^*\cs{L}\\
\cs{L} \arrow[equal]{u}{n\circ s = \id_G}  \arrow{r}{\id_{\cs{L}}} & \cs{L} \arrow[equal]{u}[swap]{p\circ s = \id_G},
\end{tikzcd}
\]
and with $n_1(h_1,h_2,g) = (h_1h_2,g)$, $n_2(h_1,h_2,g) = (h_1,n(h_2,g))$ and $p_2(h_1,h_2,g) = (h_2,g)$,
\[
\begin{tikzcd}
& \arrow[equal]{dl}{n\circ n_2=n\circ n_1} n_2^*n^*\cs{L} \arrow{rr}{n_2^*(\nu)} && n_2^*p^*\cs{L} \arrow[equal]{dr}[swap]{p \circ n_2 = n\circ p_2}& \\
n_1^*n^*\cs{L} \arrow{dr}[swap]{n_1^*(\nu)} &&&& \arrow{dl}{p_2^*(\nu)} p_2^*n^*\cs{L}\\
& n_1^*p^*\cs{L} \arrow[equal]{rr}{p\circ n_1 = p\circ p_2} && p_2^*p^*\cs{L} .
\end{tikzcd}
\]
Morphisms are morphisms in $\Loc(G)$ commuting with $\nu$.
\item Let $\CSab'(G)$ be the category of triples $(\cs{L},\nu,\mu)$ where $(\cs{L},\mu)\in \CS(G)$ and $(\cs{L},\nu)\in \Loc_{G\der}(G)$; thus, $\mu : m^*\cs{L} \to \cs{L}\boxtimes\cs{L}$ and $\nu :  n^*\cs{L} \to p^*\cs{L}$ are isomorphisms.
Morphisms in $\Loc_{G\der}(G)$ are morphisms in $\Loc(G)$ commuting with $\mu$ and $\nu$. 
\end{itemize}

@@

Let $i\der : G\der \to G$ be the kernel of $q:G \to G\ab$ and define $j : G\der \to G\der\times G$ by $j(h) = (i\der(h),1_G)$. 
For $(\cs{L},\mu,\nu)\in \CSab'(G)$, $j^*(\nu) : \cs{L}\vert_{G\der} \to (\EE)_{G\der}$ is an isomorphism. \todo{For $j^*(\nu)$ to make sense, need $j : G\der \to G\der \times G$}
This defines a functor
\[
\begin{array}{rcl}
\CSab'(G) &\to& \CSab(G) \\
(\cs{L},\mu,\nu) &\mapsto& (\cs{L},\mu,j^*(\nu)).
\end{array}
\]
Define $k: G\der\times G\to G\times G$ by $k(h,g) = (i\der(h),g)$.
Then for $(\cs{L},\mu,\beta) \in \CSab(G)$, define $\nu : n^*\cs{L} \to p_n^*\cs{L}$ \todo{I assume this should be $p^*\cs{L}$?} by
\[
\begin{tikzcd}
& n^* \cs{L} \arrow{dl}{m\circ k = n} \arrow{r} & p_n^*\cs{L} &  \\ 
k^* m^* \cs{L} \arrow{dr}{k^*(\mu)} &&& (\EE)_{G\der} \boxtimes \cs{L} \arrow[equal]{ul} \\
& k^*(\cs{L}\boxtimes\cs{L}) \arrow[equal]{r} & \cs{L}\vert_{G\der}\boxtimes \cs{L} \arrow{ur}{\beta\times 1}
\end{tikzcd}
\]
Then $(\cs{L},\mu,\nu)\in \CSab'(G)$ maps to $(\cs{L},\mu,\beta)$.
It now follows that $\CSab'(G) \to \CSab(G)$ is an equivalence. \todo{Is it easy to see why the morphisms that commute with $\mu$ and $\beta$ are the same as those commuting with $\mu$ and $\nu$?  Is this straight from the definition of the functor?}
\end{proof}

@@

>>>>

In this section we give an equivalence of categories between $\CS(G\ab)$ and $\CSab(G)$ and use it to describe
the pullback functor $q^* : \CS(G\ab) \to \CS(G)$ in terms of the forgetful functor $\CSab(G) \to \CS(G)$.

In order to study commutative character sheaves, we need some auxiliary categories.
\begin{itemize}
\item Let $\Loc(G)$ and $\Loc(G\ab)$ be the categories of local systems on $G$ and $G\ab$, respectively.
\item Let $\Loc_{G\der}(G)$ be the category of $G\der$-equivariant local systems on $G$, whose definition we now recall.
Let $n : G\der\times G\to G$ be the restriction of $m : G\times G\to G$ to $G\der\times G$,
let $p : G\der\times G \to G$ be projection to the second component, and let $s: G \to G\der\times G$ be given by $s(g) = (1,g)$.
Objects in $\Loc_{G\der}(G)$ are pairs $(\cs{L},\nu)$ where $\cs{L}$ is a local system on $G$ and
$\nu : n^*\cs{L} \to p^*\cs{L}$ is an isomorphism such that the following two diagrams commute.
\[
\begin{tikzcd}
s^*n^*\cs{L} \arrow{r}{s^*(\nu)} & s^*p^*\cs{L}\\
\cs{L} \arrow[equal]{u}{n\circ s = \id_G}  \arrow{r}{\id_{\cs{L}}} & \cs{L} \arrow[equal]{u}[swap]{p\circ s = \id_G},
\end{tikzcd}
\]
and with $n_1(h_1,h_2,g) = (h_1h_2,g)$, $n_2(h_1,h_2,g) = (h_1,n(h_2,g))$ and $p_2(h_1,h_2,g) = (h_2,g)$,
\[
\begin{tikzcd}
& \arrow[equal]{dl}{n\circ n_2=n\circ n_1} n_2^*n^*\cs{L} \arrow{rr}{n_2^*(\nu)} && n_2^*p^*\cs{L} \arrow[equal]{dr}[swap]{p \circ n_2 = n\circ p_2}& \\
n_1^*n^*\cs{L} \arrow{dr}[swap]{n_1^*(\nu)} &&&& \arrow{dl}{p_2^*(\nu)} p_2^*n^*\cs{L}\\
& n_1^*p^*\cs{L} \arrow[equal]{rr}{p\circ n_1 = p\circ p_2} && p_2^*p^*\cs{L} .
\end{tikzcd}
\]
Morphisms are morphisms in $\Loc(G)$ commuting with $\nu$.
\item Let $\CSab'(G)$ be the category of triples $(\cs{L},\nu,\mu)$ where $(\cs{L},\mu)\in \CS(G)$ and $(\cs{L},\nu)\in \Loc_{G\der}(G)$; thus, $\mu : m^*\cs{L} \to \cs{L}\boxtimes\cs{L}$ and $\nu :  n^*\cs{L} \to p^*\cs{L}$ are isomorphisms.
Morphisms in $\Loc_{G\der}(G)$ are morphisms in $\Loc(G)$ commuting with $\mu$ and $\nu$. 
\end{itemize}

@@

Let $i\der : G\der \to G$ be the kernel of $q:G \to G\ab$ and define $j : G\der \to G\der\times G$ by $j(h) = (i\der(h),1_G)$. 
For $(\cs{L},\mu,\nu)\in \CSab'(G)$, $j^*(\nu) : \cs{L}\vert_{G\der} \to (\EE)_{G\der}$ is an isomorphism. \todo{For $j^*(\nu)$ to make sense, need $j : G\der \to G\der \times G$}
This defines a functor
\[
\begin{array}{rcl}
\CSab'(G) &\to& \CSab(G) \\
(\cs{L},\mu,\nu) &\mapsto& (\cs{L},\mu,j^*(\nu)).
\end{array}
\]
Define $k: G\der\times G\to G\times G$ by $k(h,g) = (i\der(h),g)$.
Then for $(\cs{L},\mu,\beta) \in \CSab(G)$, define $\nu : n^*\cs{L} \to p^*\cs{L}$ 
%\todo{I assume this should be $p^*\cs{L}$?} by
\[
\begin{tikzcd}
& n^* \cs{L} \arrow{dl}{m\circ k = n} \arrow{r} & p^*\cs{L} &  \\ 
k^* m^* \cs{L} \arrow{dr}{k^*(\mu)} &&& (\EE)_{G\der} \boxtimes \cs{L} \arrow[equal]{ul} \\
& k^*(\cs{L}\boxtimes\cs{L}) \arrow[equal]{r} & \cs{L}\vert_{G\der}\boxtimes \cs{L} \arrow{ur}{\beta\times 1}
\end{tikzcd}
\]
Then $(\cs{L},\mu,\nu)\in \CSab'(G)$ maps to $(\cs{L},\mu,\beta)$.
It now follows that $\CSab'(G) \to \CSab(G)$ is an equivalence. \todo{Is it easy to see why the morphisms that commute with $\mu$ and $\beta$ are the same as those commuting with $\mu$ and $\nu$?  Is this straight from the definition of the functor?}
\end{proof}

@@

We start with a method that will allow us to situate the diagram in Definition \ref{def:CCS} within $\CSab(G \times G)$.
